A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Qruasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2016-01-11 mod1/response.md

We thank the referee for providing constructive and thoughtful
comments to improve the manuscipt. We have addressed all the concerns
raised by the referee and details can be found in the revised version
-- please see attached. A brief description on how we incoprated the
changes can be found below.

# Major comments
1:
- There is already a lensing model in H14 (a paper the authors refer
  to numerous times) and it is unclear why they redid the lensing
  model (they use the same SMA data as H14 but a different code). If
  the derived model is significantly different from H14 then this
  should be highlighted otherwise the lens modeling section isn't
  necessary in this paper.

> Most parameters obtained in our new analysis with our new lensing
  code are indeed consistent with the earlier model reported by H14,
  such that the results are only slightly improved. However, H14 did
  not report the full range of best-fit parameters and uncertainties
  in their analysis, such that our results are significantly more
  detailed. To take this comment into account, we thus significantly
  shortened the text in this section by removing details on the lens
  modeling approach (and including a reference to the literature
  instead), and we have moved the lens mass and consistent results
  into Table 1 - which is used to briefly summarize the full range of
  parameters. This includes the important inferred half-light radius,
  which is used later in the analysis.

-- we need to say explicitly what the different parameters are in this
   paper - without that it is not possible to understand.

2:
- The SMG is thought to harbor a luminous AGN. In that case, the LIR
  will certainly have a contribution from the AGN that should be
  accounted for otherwise the SFR will be overestimated: see
  e.g. Coppin+2010, Kirkpatrick+2012, Magdis+2013,
  Kirkpatrick+2014. Please correct LIR for the AGN emission prior to
  estimating SFR and include an AGN component in the SED fitting.

> In our analysis, we fit SED models to the rest-frame FIR, which has
  been found to have negligible AGN contribution to rest-frame FIR (≥
  60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15). Since we do
  not have MIR measurements solely from the background SMG and due to
  the postive K corretion blueward of dust peak, the forground radio
  galaxy contributes a non-negligible amount to the MIR luminosity, we
  therefore didn't fit an AGN component. Including an additional
  component, and thus free parameters to the SED model will be
  over-fitted due to the limited amount of data at hand. Instead our
  SED model includes a power-law to the blue side of the dust peak,
  which accounts for the MIR excess and allows us to estimate the IR
  luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12). We
  derived the SFR and other corresponding properties using the L_FIR,
  (45-122.5), which is mostly due to SF-driven dust emission.

-- briefly discuss this in the text.

3:
- section 4.3 is way too wordy and can be cut down to a few paragraphs
  and a table summarizing these key values (already given in Table
  4). These are all standard calculations and you can refer to CW14
  for the equations rather than repeating them here.

> We removed standard equations from the manuscript, and combined the
  sections reporting SFE, SFR, and SFRSD into one. We also shortened
  the section.

4:
- You should also summarize the evidence for the AGN in this SMG
  (maybe when you mention this in the intro) so the reader doesn't
  have to read H14.

> We rephrased the introduction to show more clearly the evidence of
  an AGN.

5:
- [a further concern/question about Table 4 is whether all the same
  assumptions such as excitation, alpha_co, etc. were made for the
  other SMGs otherwise the comparisons are meaningless]

> We added notes in the caption of Table 4 to recap all assumptions
  used in deriving these quantities.

@@

6:
- Section 5: why do the authors cherry-pick these 2 SMGs to make
  comparisons? there are many other sources that could be chosen with
  a range of properties. A comparison to these 2 SMGs is not useful at
  all given the diversity in this population (e.g. the sentence "This
  demonstrates the large ..." is not true when comparing only 3
  objects). I suggest comparing to the general properties observed for
  SMGs (as summarized in CW14 or Casey+14) which will be more useful
  in placing this object in the context of the SMG population.

> We picked out two apparently similarly bright gravitationally lensed
  SMGs to show the ranges of SMGs properties, of which intrinsically
  sit at faint ends of the luminosity distribution, and thus would not
  have been studied in sensitivity-limited samples. In addition, these
  are among the SMGs which are best-studied to date and their
  properties are deriving using similar approach in this paper. Hence,
  a comparison with these object will have relatively lower
  uncertainties. We have added a compilation of SMG and type-2 QSOs
  properties to the Table. Please see the table notes and comments for
  details. We have incoporated a comparison to these sample-averaged
  values in our conclusion as well.

-- need to re-write this. we would have seen at least two of these in
   unlensed samples. just comparing since these are the most
   well-known ones that similarly stick out from their submm fluxes
   (>400mJy).

   - differential lensing and ratios 
   - if source is intrinsically fainter 
   - write how we address issue raised --> reasons why we kept

@@

## 7
- the discussion/conclusions should focus on what is new from this
  paper and not what is already presented in H14. E.g. the last
  sentence about this SMG transitioning from starburst to QSO
  phase. How is that conclusion made or strengthened with this new
  data?

> We updated the conclusions.

# Minor comments
1:
- the depletion time seems short compared to other SMGs which are
  ~100Myr although maybe it is consistent with other SMGs with AGN in
  them.

> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs,
  please see also Table 4.

2:
- section headings in 3 are strange. Remove the words "New results"
  since this is obvious and a requirement for publication. Also remove
  subheading or second line in heading 3.2.

> We removed "New results" in the subject headings.

3:
- the left panels on Fig 1 and 2 should show the same region (have the
  same RA/DEC axes). It is also tough to tell by eye if the VLA9GHz
  and SMA emission is coincident. Perhaps these can be overlayed on
  Fig 1.

> We adjusted the panel sizes as suggested, and marked the locations
  of the peak emission from the SMA as white crosses on the right
  panel in Figure 1.

4:
- figure 3: orange is difficult to see. What is the SNR of the
  residuals in the right panel?

> We modified our caption to state that the quoted contour levels are
  the same for both panels in the figure. We changed the critical line
  color to green for better readability.

5:
- figure 4: again colors (red, orange) are hard to distinguish on a
  print out version of the paper.

> We did not use orange in this figure. Please kindly clarify.

6:
- specify the wavelengths range assumed for FIR.

> We mentioned the FIR range (42.5-122.5 micron) in Section 4.2.2.

7:
- last para section 4.2.2: it is limited data in the submm not the FIR
  [need to be probing Rayleigh Jeans] that makes the dust mass weakly
  constrained. I don't understand what the last sentence in this para
  means - I think there are words missing.

> We clarified this issue by adding the phrase "rest-frame" to FIR. We
  also restructured the last paragraph to convey our message more
  clearly.

8: 
- SF surface density: from resolved studies of SMGs is it reasonable
  to divide half the SFR and gas mass by the area out to the
  half-light radii? give appropriate references to justify this
  assumption.

> We now provide a few citations to show that this is a common
  assumption.

9:
- intro: the first para makes it sound like our knowledge of SMGs
  comes primarily from SMGs found in large sky Herschel surveys and
  SPT but this is not true. Please include references to earlier work
  that established the basic properties of SMGs (redshift
  distribution, luminosities, SFRs, Mgas, etc) prior to Herschel even
  launching.

> We restructured the paragraph and added earlier discoveries.

-- probably wants smail+97,hughes+98,barger+98 or so here

10:
- the fact that the lensing system has two components isn't presented
  clearly in this paper. I had to read H14 to understand what the
  authors meant when they mentioned companion B. Please make this
  clearer so the reader does not have to read H14

> We added a sentence to elaborate on this, please see the revised
  manuscript.

-- say where - intro

11:
- last few paras of paper: what does "breaking up its dust cocoon"
  mean? this is the first time this is mentioned and should be
  explained if it is relevant.

> We mentioned this as a reference from Haas+14. We have removed this
  phrase in the revised version given that this has been mentioned in
  Haas+14, and is not necessary in our discussion.

12:
- end of section 4.3.1: the factor of 2 for dust mass is overshadowed
  by the factor of >5 in alpha_co

> We removed that sentence.

13:
- related to depletion time, there is a new Nature paper by Narayanan
  et al (published Sept 23) which discusses how SMGs in sims can last
  for a Gyr with replenishment from the IGM. In that case, is the
  depletion timescale really useful? what do we learn if the galaxy is
  getting new gas?

>The derived depletion timescale is derived the based on the
 definition of the quantity τ = Mgas/SFR, which descibes the time it
 would take for a galaxy to use up the available molecular gas
 reservoir given the current star formation rate, assuming no
 replenishment of gas (Carilli & Walter 2013). Hence, this quantity
 provides a lower limit on the timescale for SF activity. Based on our
 observations, we find no evidence of gas inflow in SMMJ0939.

13:
- dynamical mass calculation: can you estimate how much higher this
  would be given observations showing the different radii between the
  molecular and dust emission in SMGs. How different are the radii?

>The half-light radii of dust-emitting regions in SMGs typically are ~
 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870
 µm data for 52 SMGs. Tacconi+06 report a median FWHM size of 4.1 ±1.6
 kpc based on high-J CO measurements. Given the small number
 statistics on resolved CO(1-0) emission in QSOs, where Riechers+11
 find no evidence of extent cold gas emission, we did not include an
 additional estimate of the dynamical mass assuming some physical size
 from recent observations (still limited) in the paper. However, we
 have noted these physical sizes in the text, which allows readers to
 scale the dynamical mass correspondingly should they wish to do
 so. Please see the revised manuscipt.

14:
- appendix: "no evidence of correlation" do the authors mean
  "covariance" here?

> We used the word "correlation" to indicate that regardless of the
  variation found in dust mass due to a different prior imposed on the
  emissivity, the IR luminosity is insensivtive to such changes in
  dust mass. Both the dust mass and IR lumonisty are inferred from the
  best-fit SED model, and are not parameters in the model (and the
  loss function). For these reasons, we do not mean the covariance
  here.

### 2016-01-13 mod1/manuscript/ms.tex
added in DR's comments

\documentclass[iop, revtex4]{emulateapj}
\usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}} 
\newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}
\newcommand\tnl{\,\tablenotemark{l}}

\slugcomment{Submitted to the ApJ, Revised version December 20, 2015}
\usepackage{amsmath}
\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

\begin{document}
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using
the Combined Array for Research in Millimeter-wave Astronomy. 
SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
The 104~GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
 a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
 This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
Our comparative study
of the gas mass, dust mass, star formation rate, and surface densities in SMM
J0939+8315
and other high-redshift SMGs and type-2 quasars 
{\bf shows that it is consistent with the properties of both populations. Together with the presence of its obscured quasar, massive molecular gas reservoir, on-going intensive star-formation and the short gas depletion timescale suggests that
SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase. }
\end{abstract}
\keywords{cosmology: observations --- galaxies: evolution --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
{\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
%This galaxy population was first detected 
%$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
%Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
Previous works %following this discovery
have shown that SMGs
 are extremely luminous in the infrared
 wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates (SFR) \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
{\bf Following the pioneering works in the discovery of this population}, considerable amounts of effort have been invested into 
obtaining large samples of SMGs by carrying out
  large sky surveys with (sub)-mm facilities such as the {\it Herschel Space Observatory} \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}.  
  }

@@

Many recent detailed studies have been carried out on SMGs that are gravitationally lensed,
 as lensing amplifies the intrinsic fluxes of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with the {\it Herschel Space Telescope}, in which
a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley
Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
companion galaxy B at $z$\,=\,0.685{\bf, where this companion galaxy is identified by \citeauthor{Haas14} (2014; hereafter H14) via observations with the Keck II Observatory and the {\it Hubble Space Telescope}.}
SMM\,J0939 is currently one of the brightest known lensed
SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
{\bf Previous detections of C~{\scriptsize\sc IV}~1459\AA\
 and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
 placed the redshift of this galaxy at $z$\,=\,2.221. Based on the line fluxes and spectral line widths of these AGN lines, H14 suggested the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens}
To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. Lens modeling is carried out in the visibility
({\it uv-}) plane using an updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}, details of the parametric lens model can be found in \citet{Bussmann15a}. 
%In the code, the surface mass densities of both
%lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
%elliptical Gaussian profile.

@@

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
{\bf  Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
%, this is consistent the value reported by H14 within the errors. 
and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
All best-fit
parameters are listed in Table~\ref{tab:lensParam}. 
%The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
%the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
\input{table_lensParams}

@@

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
case. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a FIR luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
\micron$ \citep{Dunne03a}, we find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun{\bf ;} the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$). These properties are derived based on the SED fitting to the photometric data, \ie prior
to lensing correction.{\bf We note that the dust mass is weakly constrained owing to the dearth of data in the {\bf rest-frame} FIR waveband. As such, we investigate how the dust mass would be affected by fitting an additional optically thick model with an upper limit of 
 $\beta$ adjusted from 2.2 to 3.0. While the difference in each best-fit parameter between this scenario and the previous model (an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.}
\subsection{Physical Properties of the ISM in SMM\,J0939}

>>>>

\documentclass[iop, revtex4]{emulateapj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{amsmath}

\usepackage{etoolbox}

\makeatletter

% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}

% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}

\makeatother

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}} 
\newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}
\newcommand\tnl{\,\tablenotemark{l}}

\slugcomment{Submitted to the ApJ}
\input{changelog.tex}       % git revision hash, new command

\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

\begin{document}
{\tiny  \RevisionInfo}        % place it here
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Qruasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using
the Combined Array for Research in Millimeter-wave Astronomy. 
SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
The 104~GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
 a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling.
 % performed on the 1\,mm continuum emission.
 This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
{\bf 
We find that the properties of the interstellar medium of
 SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the 
evolutionary link model, according in which this SMG represents an intermediate stage of present-day galaxies
at an earlier epoch. 
 }
\end{abstract}
\keywords{cosmology: observations --- galaxies: evolution --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
{\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
%This galaxy population was first detected 
%$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
%Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
Previous works %following this discovery
have shown that SMGs
 are extremely luminous in the infrared
 wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates \citep[SFR $\gtrsim$\,500\,\Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
{\bf Following the pioneering works in the discovery of this population \citep{Barger98a,Smail97a,Hughes98a}}, considerable amounts of effort have been invested into 
obtaining large samples of SMGs by carrying out
  large sky surveys with (sub)-mm facilities such as the {\it Herschel Space Observatory} \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}.  
  }

@@

Many recent detailed studies have been carried out on SMGs that are gravitationally lensed,
 as lensing amplifies the intrinsic fluxes of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with {\it Herschel}, in which
a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley
Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 {\bf at $z$\,=\,0.685, which has a
companion galaxy B as seen in Keck 2$\micron$ and the {\it Hubble Space Telescope} 702nm images \citep[hereafter H14]{Haas14}}.
SMM\,J0939 is currently one of the brightest known lensed
SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
{\bf Detections of C~{\scriptsize\sc IV}~1459\AA\
 and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
 placed the redshift of this galaxy at $z$\,=\,2.221. Based on the line fluxes and spectral line widths of these AGN lines, H14 suggest the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens}
To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. 
Lens modeling is carried out in the visibility
({\it uv-}) plane using an updated version the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
details of the parametric lens model can be found in \citet{Bussmann15a}. 
{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B as mentioned in Section~\ref{sec:intro}, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
elliptical Gaussian profile. }

@@

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
{\bf  Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
All best-fit
parameters are listed in Table~\ref{tab:lensParam}. 
\input{table_lensParams}

@@

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of optically thin
models corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of optically thick models
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
case. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
^{12}$\,\Lsun
\footnote{
Owning to the positive K-correction blue-ward of the dust peak, in which 
the foreground radio galaxy contributes a non-negligible amount to the MIR luminosity, we do not fit an AGN component.
Instead, we adopt a power-law to account for the MIR excess, which allows us to estimate the IR
luminosity \citep{Casey12a, Riechers13a, Kirkpatrick15a}. }. 
Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
\micron$ \citep{Dunne03a}, we find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun{\bf ;} the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$). These properties are derived based on the SED fitting to the photometric data, \ie prior
to lensing correction.{\bf We note that the dust mass is weakly constrained owing to the dearth of data in the {\bf rest-frame} FIR waveband. As such, we investigate how the dust mass would be affected by fitting additional optically thick models with an upper limit of 
 $\beta$ adjusted from 2.2 to 3.0. While the difference in each best-fit parameter between this scenario and the previous models (with an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.}
\subsection{Physical Properties of the ISM in SMM\,J0939}
